Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-11 paper.tex
cleanup whitespace
update table template for shabbyreal denoising metrics
Update paper.tex
- Remove ImageOverlay since we are not using that.
- Added NoiseGenerator.

\smallskip
\noindent\textbf{\texttt{ImageOverlay}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for ``printing" or applying other artifacts like staples or stamps.

@@

\begin{table}
\centering
\caption{Model training statistics and performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & PSNR & SSIM & RMSE\\
\hline
Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
Augraphy\_NAFNet & & &
Augraphy\_NAFNet_large & & &
\hline
\end{tabular}
\end{table}

>>>>

\smallskip
\noindent\textbf{\texttt{OverlayBuilder}.} ~This class uses various blending algorithms to fuse foreground and background images together, which is useful for ``printing" or applying other artifacts like staples or stamps.

\smallskip
\noindent\textbf{\texttt{NoiseGenerator}.} ~This class uses make blobs algorithm to generate mask of noises in different shape and location.

@@

\begin{table}
\centering
\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & Score \\
\hline
SSIM & \\
PSNR & \\
RMSE & \\
\hline
\end{tabular}
\end{table}
